documentclass{article} \usepackage[utf8]{inputenc} \usepackage{titling} \title{Team Star Project \ \large Architecture Design and UI} \author{Mubarak, Ayantayo Tim, Josh, and Jack} \date{10/9/2024}

\begin{document}

\maketitle

\section{Architecture} \subsection{The architecture for our project will be web-based MVC, enabling a user-friendly interface and effective \ moderation. This is crucial for building a widely accessible application that can accommodate a vast user base.} \subsection{We will implement a top-down class structure that emphasizes isolated classes and functions. This will facilitate the breakdown of each data structure into its base elements, minimizing dependencies during the development of an interconnected card game for multiple users.} \subsection{We are particularly concerned about effectively managing the inevitable dependencies that will arise, especially concerning the lobby and server systems.}

\section{Technology} \subsection{Our primary technology stack will be based on Java with additional Java-adjacent plugins, tools, and server hosting utilized from our onboarding and individual assignments.} \subsection{Notable technologies will include Firebase for server database interactions, which will support data persistence necessary for our game.} \subsection{We have chosen JUnit as our testing framework due to its extensive documentation and our prior experience, enhancing our comfort and capability to integrate it into the project.}

\section{Persistent Data} \subsection{All long-term data will be stored in a Firebase database, with team members proficient in manipulating data and its structures.} \subsection{Each user will have a data package linked to their username, serving as a key for authentication and enabling comparison of historical data with current records during login and game interactions.}

\section{User Stories} \subsection{Our development will prioritize the following user stories, ensuring each functionality aligns with user expectations:}

\begin{itemize} \item As a User, I want to start the game identically for a fair experience. \item As a User, I want to call BS on other players to determine if they were lying. \item As a User, I want to place my cards to reduce my hand. \item As a User, I want to flip the top three cards after BS is called for verification. \item As a User, I want to collect cards and add them to my deck to ensure game integrity. \item As a User, I want a tutorial to explain the game and the option to review it later to enhance my understanding. \item As a User, I want the game to have a purple theme to reflect my preferences. \item As a User, I want the game to look futuristic and neon bright for visual appeal. \item As a User, I want options for guest access and registered accounts for personalized experiences. \item As an Admin User, I want tools to manage users, edit information, and maintain the game environment. \end{itemize}

\section{Coding Standards} \subsection{Our team is committed to adhering to strict coding standards to ensure readability and functionality. This includes: } \begin{itemize} \item Never pushing non-functional code; only pushing commented-out code when absolutely necessary for reference. \item Utilizing unique variable names to avoid ambiguity and improve clarity within the codebase. \end{itemize}

\subsection{We emphasize thorough documentation for every code commit, detailing the purpose and functional changes made. This practice will ensure that all team members remain informed about modifications to functions or classes, fostering collaboration and understanding.}

\end{document}
